%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Lau CV
% LaTeX Template
% Version 1.0 (18/7/21)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	Packages and other document configurations
%----------------------------------------------------------------------------------------

% compile with latexmk -xelatex H.Sherry-Zhang.tex
\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)
\include{sherryzhang-template} % Include sherryzhang-template.tex which contains packages and document layout definitions
\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether
\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

%\begin{CJK}
    \name{H. Sherry Zhang} %\hspace{0.25cm} \zh{张慧泽}}
%\end{CJK}
\hfill
update: 2025-09
\spacedhrule{0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

\vspace{0.25cm}
\noindent
\href{mailto:hsherryzhang@utexas.edu}{hsherryzhang@utexas.edu}
\hspace{4em}
\href{https://github.com/huizezhang-sherry/}{Github: huizezhang-sherry}
\hfill
\href{https://huizezhangsh.netlify.app/}{https://huizezhangsh.netlify.app/}




%----------------------------------------------------------------------------------------
\roottitle{Appointment}
%----------------------------------------------------------------------------------------
\secentry{University of Texas at Austin}{2024}{present}
    {Postdoctoral Fellow working with Prof. Roger Peng
    }
%------------------------------------------------

%----------------------------------------------------------------------------------------
\roottitle{Education}
%----------------------------------------------------------------------------------------
\secentry{PhD in Statistics, Monash University}{2020}{2023}
    {Thesis: \textit{New tools for visualising and explaining multivariate spatio-temporal data},
    supervised by Prof. Dianne Cook, Dr. Patricia Men\'endez, Dr. Nicolas Langren\'e, and Dr. Ursula Laa 
    }

\secentry{BComm(Hons.), Monash University}{2016}{2019}
    {Bachelor of Commerce with Honours, First Class Honours (H1) \newline
    Thesis: \textit{Exploration of judicial facial expression in videos of legal proceedings}, supervised by Prof. Dianne Cook and Prof. Russell Smyth
    }
%------------------------------------------------

%----------------------------------------------------------------------------------------
\roottitle{Awards}
%----------------------------------------------------------------------------------------
\twocolumnentry{Winner of the JSM Annual Data Challenge Expo}{2025}
\twocolumnentry{John M. Chambers Statistical Software Award (ASA section of statistical computing), awarded for the R package cubble, which introduces a new data structure for spatio-temporal data and provides a ggplot2 extension for creating glyph maps.}{2024}
\twocolumnentry{Opportunity scholar, Posit::conf(2023)}{2023}
\twocolumnentry{People's Choice Award, ECSS Miniconference, Statistical Society of Australia}{2022}
\twocolumnentry{Postgraduate (PhD) Research Scholarship, CSIRO Data61}{2020 - 2023}
\twocolumnentry{Co-Funded Graduate Research Scholarship, Monash Business School}{2020 - 2023}
\twocolumnentry{Dean's Honours List, Monash Business School}{2020}
\twocolumnentry{Summer Vacation Research Scholarship, Monash University}{2019}


\vspace{-1em}
%----------------------------------------------------------------------------------------
\roottitle{Publications}
%----------------------------------------------------------------------------------------
\begin{enumerate}[itemsep=0.1em]

    \item \underline{\textbf{Zhang, H. S.}}, Cook, D., Laa, U., Langren\'e, N., \& Men\'endez, P. (2025). 
    A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes 
    from Multivariate Data. \emph{Journal of Computational and Graphical Statistics}, 
    \emph{1-19}. \url{https://doi.org/10.1080/10618600.2024.2374960}

    \item \underline{\textbf{Zhang, H. S.}}, Cook, D., Laa, U., Langren\'e, N., \& Men\'endez, P. (2024). 
    cubble: An R package for organizing and wrangling multivariate spatio-temporal data. 
    \emph{Journal of Statistical Software}, \emph{110}, 1-27. \url{https://doi.org/10.18637/jss.v110.i07}
    
    \item Lee, S., Cook, D., Silva, N. da, Laa, U., Spyrison, N., Wang, E., \& 
    \underline{\textbf{Zhang, H. S.}} (2022). The state-of-the-art on tours for 
    dynamic visualization of high-dimensional data. \emph{WIREs Computational Statistics}, 
    \emph{14}(4), e1573. \url{https://doi.org/10.1002/wics.1573}
    
    \item \underline{\textbf{Zhang, H. S.}}, Cook, D., Laa, U., Langren\'e, N., \& Men\'endez, P. (2021). 
    Visual Diagnostics for Constrained Optimisation with Application to Guided Tours. 
    \emph{The R Journal}, \emph{13}(2), 624--641. \url{https://doi.org/10.32614/RJ-2021-105}
    

\end{enumerate}

% \noindent\textit{Accepted:}\vspace{-0.5em}
% \begin{enumerate}[resume]

    % \item \textbf{Zhang, H. S.}, Cook, D., Laa, U., Langren\'e, N., \& Men\'endez, P. (2024). 
    % \textit{cubble: An R package for organizing and wrangling multivariate spatio-temporal data}. 
    % \emph{Accepted by the Journal of Statistical Software}. 
    % \url{https://doi.org/10.18637/jss.v110.i07 }
% 
% \end{enumerate}

\noindent\textit{Submitted:}\vspace{-0.5em}
\begin{enumerate}[resume]

    \item \underline{\textbf{Zhang, H. S.}}, Peng, R. D.(2024). Inside Out: Externalizing Assumptions 
    in Data Analysis as Validation Checks. \emph{Accepted in the Journal of Data Science pending on minor revision}. 
    \url{https://arxiv.org/abs/2501.04296}

    \item \underline{\textbf{Zhang, H. S.}}, Cook, D., Langren\'e, N., \& Leung, J. W. Y. (2025). 
    Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding 
    Optimization Choices. \emph{Submitted to the Journal of Computational and Graphical 
    Statistics}. \url{https://arxiv.org/abs/2407.13663}
    
    \item \underline{\textbf{Zhang, H. S.}}, Peng, R. D.(2025). An LLM-based Pipeline for 
    Understanding Decision Choices in Data Analysis from Published Literature. 
    \emph{Submitted to The ACM CHI conference on Human Factors in Computing Systems (CHI 2026)}. 
    \url{https://github.com/huizezhang-sherry/paper-decisions}
    
  
\end{enumerate}

%----------------------------------------------------------------------------------------
\roottitle{Software Activities}
%----------------------------------------------------------------------------------------

\noindent\textit{Package maintainer (primary author):}

\vspace{0.5em}

\twocolumnentries{A general data pipeline for computing indexes}{tidyindex} \newline 
\twocolumnentries{A data structure for organizing and wrangling spatio-temporal data, 52 stars on GitHub}{cubble} \newline
\twocolumnentries{Visual diagnostics plots for projection pursuit guided tour optimisation}{ferrn} \newline 

\vspace{1em}
\noindent\textit{Package contributor:}

\vspace{0.5em}
\twocolumnentries{Tools to help the associate editors with the reviewing process of the R journal}{rj} \newline
\twocolumnentries{Tools for authors to write, check, and submit articles to the R Journal, 30 stars on GitHub}{rjtools} \newline
\twocolumnentries{Tour methods for multivariate data visualisation, 62 stars on GitHub}{tourr}

\vspace{0.5em}

\noindent\textit{Other activities:}

\vspace{0.5em}

\twocolumnentries{maintainer of CRAN task view: Dynamic Visualizations}{2024} \newline 
\twocolumnentries{reviewer of ROpenSci software peer review}{2024} \newline 
\twocolumnentries{reviewer of John M. Chambers Statistical Software Award 2025}{2024} \newline 
\twocolumnentries{contributor to fix bug in base R on array max.print}{2025} \newline 

\vspace{1em}



%----------------------------------------------------------------------------------------
\roottitle{Talks}
%----------------------------------------------------------------------------------------

\talkentry{NYU-LMU-Workshop Making Data Work: Tools for Better Stats. Practice}{Munich, Germany}{2025 Jun}
\talkentry{Joint Statistical Meeting (JSM)}{Nashville, USA}{2025 Aug}
\talkentry{Symposium on Data Science and Statistics}{Salt Lake City, USA}{2025 May}
\talkentry{University of Nebraska-Lincoln Graphic Group}{virtual}{2024 Dec}
\talkentry{UT Austin SDS Department Seminar}{Austin, USA}{2024 Oct}
\talkentry{Intl. Conf. on Trends \& Perspectives in Linear Stats. Inference (LinStat 2024)}{Poprad, Slovakia}{2024 Sep}
\talkentry{Computational Statistics (COMPSTAT 2024)}{Giessen, Germany}{2024 Aug}
\talkentry{Joint Statistical Meeting (JSM)}{Portland, USA}{2024 Aug}
\talkentry{John M. Chambers Statistical Software Award Talk}{Portland, USA}{2024 Aug}
\talkentry{Humboldt University of Berlin, Faculty of Economics}{Germany}{2024 Jan}
\talkentry{Computational and Methodological Statistics (CMStatistics 2023) }{Berlin, Germany}{2023 Dec}
\talkentry{Monash Research Tools Workshop}{Melbourne, Australia}{2023 Sep}
\talkentry{University of M\"{u}nster, Institute for Geoinformatics}{Germany}{2023 May}
\talkentry{The Australian Spatial Econometrics and Statistics Workshop}{Melbourne, Australia}{2023 Feb}
\talkentry{Maynooth University, Department of Mathematics and Statistics}{Ireland}{2023 Apr}
\talkentry{CANSSI Ontario Statistical Software Conference \(invite\)}{virtual}{2022 Nov}
\talkentry{Early Career and Student Statisticians Miniconference}{virtual}{2022 Nov}
\talkentry{UseR! 2022}{virtual}{2022 Jun}
\talkentry{UseR! 2021}{virtual}{2021 Jul}
\vspace{-1em}


%----------------------------------------------------------------------------------------
\roottitle{Teaching and Supervision}
%----------------------------------------------------------------------------------------

\noindent\textit{Instructor for UT Austin undergraduate coursework: }\vspace{-0.5em}

\vspace{1em}

\twocolumnentry{SDS322E Elements of Data Sciences}{2025 Fall}

\noindent\textit{Research supervision: }\vspace{-0.5em}

\vspace{1em}

\twocolumnentry{Co-supervisor for Google Summer of Code R Project: ribbon and segment glyph map}{2024 summer}
\twocolumnentry{Co-supervisor first year PhD student summer research at University of Texas at Austin}{2024 summer}


\noindent\textit{TA for Monash undergraduate and graduate coursework: }\vspace{-0.5em}

\vspace{1em}

\twocolumnentry{ETC5512 Wild Caught Data}{2021, 2022}
\twocolumnentry{ETC5521 Exploratory Data Analysis}{2020, 2021}
\twocolumnentry{ETC1010/ETC5510 Introduction to Data Analysis}{2019, 2020}

\vspace{0.5em}

\noindent\textit{Instructor for workshops: }\vspace{-0.5em}

\vspace{1em}

\twocolumnentry{Switching between space and time: Spatio-temporal analysis with cubble, R Ladies Vienna }{2023 Apr}
\twocolumnentry{Wrangling spatio-temporal data with R, WOMBAT \href{https://sptm-tidy.numbat.space/}{link}}{2022 Dec}
\twocolumnentry{Switching between space and time: Spatio-temporal analysis with cubble, R Ladies Melbourne}{2022 Sep}

%----------------------------------------------------------------------------------------
\roottitle{Service}
%----------------------------------------------------------------------------------------
\twocolumnentry{Program Chair-Elect ASA Section of Statistical Graphics}{2025}
\twocolumnentry{Reviewer for the R Journal, The Australian \& New Zealand Journal of Statistics, ROpenSci}{2024 onwards}
\twocolumnentry{John M. Chambers Statistical Software Award review panel}{2024}
\twocolumnentry{Seminar organiser: Monash NUMBATs}{2022}

%----------------------------------------------------------------------------------------
\roottitle{Media Coverage}
%----------------------------------------------------------------------------------------
\twocolumnentry{Monash Graduate research impact: \href{https://www.monash.edu/business/research/graduate-research-program/phd-programs/graduate-research-impact/crunching-the-numbers-how-new-research-has-revealed-the-hidden-truth-behind-indexes}{Crunching the numbers: How new research has revealed the hidden truth behind indexes}}{2023}



\end{document}